\subsection{Elevation}
\subsubsection*{Data Source}
\begin{itemize}[nolistsep]
\item \textbf{Contact}
\item \textbf{Citation/Link}
\item \textbf{Data (local)}
\item \textbf{Geographic Extent}
\item \textbf{Temporal Extent}
\item \textbf{Acknowledgment}
\end{itemize}
\subsubsection*{Brief Description}

Elevation can influence PM\textsubscript{2.5} concentrations; for example, PM\textsubscript{2.5} can accumulate in mountain valleys during persistent cold air pools 
(commonly referred to as inversions) 
during winter \citep{Whiteman2014}. We will get elevation data from the 3D Elevation Program, which has resolution of 1/3 arc-second. This resolution is approximately 10 m north/south and varies east/west with latitude \citep{USGSElevation2017}.

\subsubsection*{Notes}
\subsubsection*{File Format}
\subsubsection*{Data Filtering and Processing}
\subsubsection*{Final Variable(s)}
\subsubsection*{Methods}
\begin{enumerate}
\item  \underline{Step 1: Download Data for Study Area}\\\\
Navigate to the \href{https://viewer.nationalmap.gov/basic/?basemap=b1\&category=ned,nedsrc\&title=3DEP\%20View}{3D Elevation Program (3DEP) The National Map Viewer}. Only the "1/3 arc-second DEM" filter should be selected. The file format should be ArcGrid. Click "Find Products". Click "results" for the Elevation Products (3DEP). Add all results to cart. Click "View Cart". Click "Export Items to CSV". Save downloaded CSV. Run script "NED\_bulk\_download.py". Pass the location of the CSV file as the first argument and the desired save path as the second argument.
\end{enumerate}
\subsubsection*{Quality Control}
\subsubsection*{Script Names}
\begin{enumerate}
\item NED\_bulk\_download.py
\end{enumerate}
\subsubsection*{Data File Names}
\begin{enumerate}
\item NED\_bulk\_download\_file\_list.csv
\end{enumerate}