\clearpage
\subsubsection{\texorpdfstring{PM\textsubscript{2.5}}{} data from the Fire Cache Smoke Monitor Archive}

\subsubsection*{To Do}

\begin{enumerate}
\item follow up about password protected monitor data (10 sites, see below)
\item also figure out if all of 2018 data is there and ask when that will be complete if it isn't
\end{enumerate}

\subsubsection*{Data Source}

\begin{itemize}[nolistsep]
\item \textbf{Contact} Josh Walston at 775-673-7624; Amber Ortega directed us to the website and Scott Landis suggested that a good person to contact about the page would be Mike Broughton from the US Forest Service (\url{michaelbroughton@fs.fed.us})
\item \textbf{Citation/Link} \url{https://wrcc.dri.edu/cgi-bin/smoke.pl}
\item \textbf{Data (local)} PM\textsubscript{2.5} data from the Fire Cache Smoke Monitor Archive
\item \textbf{Geographic Extent}
\item \textbf{Temporal Extent}
\item \textbf{Acknowledgment}
\end{itemize}

\subsubsection*{Brief Description}

\subsubsection*{Notes}

Several of the files were password protected, so we contacted Josh and they were able to unlock most of them. As of March 20, 2018, only "Smoke NCFS E-BAM \# 3 is still password protected. (Need to try calling Josh again.) Here are some comments that the system administrator passed along to us (via Josh): the data does not get quality controlled, so we should do our own qa/qc. The monitors/data were designed for the fire community to see data in real time, not for research purposes. If we want to speak with the people who ran the monitors, we should contact Josh and the director can probably put us in contact.

Update 2018-05-2018: sent email to Josh requesting the ``Smoke NCFS E-BAM \# 3'' data with flags and with the other formatting settings we used on the other files. Also asked how to determine which datum is assoiciated with the latitude/longitude data.

% %Several of the files we would like to download are currently password protected. We've been in contact with Josh at 775-674-7010. Melissa called on March 15, 2018 and he will email the system administrator to request that the password protection be removed.
% 
% %Files Fire\_Cache\_Smoke\_DRI\_Smoke\_E-BAM\_231.csv and 
% %Fire\_Cache\_Smoke\_DRI\_Smoke\_E-BAM\_866.csv were deleted because it only had data across 3 days, but none of them met the basic requirements to be put into the final data (e.g., not enough observations or negative concentrations).
% 
% %Fire\_Cache\_Smoke\_DRI\_Smoke\_E\_BAM\_65.csv was also deleted because it only had 5 data points across 2 days, and we are requiring at least 18 hourly data points within a day to be put into the final data.
% 

%These monitors were not included because the website indicated that it did not have data during our study period (January 1, 2008 - December 31, 2014):
%\begin{enumerate}[nolistsep]
%\item Smoke E-BAM 418
%\item Smoke E-BAM 591
%\item Smoke E-BAM 592
%\item Smoke E-BAM 882
%\item Smoke E-BAM 969
%\item Smoke USFS R2-922
%\item Smoke USFS R2-923
%\item Smoke USFS R2-924
%\item Smoke USFS R8-34
%\item Smoke USFS R8-35
%\item Smoke USFS R8-55
%\item Smoke USFS R8-56
%\item Smoke USFS 3015
%\item Smoke USFS 3016
%\item Smoke USFS R9-3017
%\item Smoke USFS R9-3018
%\item RSF Smoke Monitor 1
%\item Lolo NF Smoke Monitor \#1
%\item Lolo NF Smoke Monitor \#2
%\end{enumerate}

\subsubsection*{File Formats}
.csv

\subsubsection*{Data Filtering and Processing}

\subsubsection*{Final Variable(s)}

\subsubsection*{Methods}

\begin{enumerate}[nolistsep]
\item
\item
\end{enumerate}

\subsubsection*{Quality Control}

\subsubsection*{Script Names}

\begin{enumerate}[nolistsep]
\item
\end{enumerate}

%\subsubsection*{Original Data File Names and notes about monitors}

%\begin{enumerate}[nolistsep]
%\item Fire\_Cache\_Smoke\_DRI\_Cache-NCFS-EBAM\#3-with-flags.csv
%\item Fire\_Cache\_Smoke\_DRI\_FWS\_Smoke\_N1.csv
%\item Fire\_Cache\_Smoke\_DRI\_Smoke\_N11.csv
%\item Fire\_Cache\_Smoke\_DRI\_Smoke\_N13.csv
%\item Fire\_Cache\_Smoke\_DRI\_Smoke\_N15.csv
%\item Fire\_Cache\_Smoke\_DRI\_Smoke\_N16.csv
%\item Fire\_Cache\_Smoke\_DRI\_Smoke\_N17.csv
%\item Fire\_Cache\_Smoke\_DRI\_Smoke\_N19.csv
%\item Fire\_Cache\_Smoke\_DRI\_Smoke\_N20.csv
%\item Fire\_Cache\_Smoke\_DRI\_Smoke\_N21.csv
%\item Fire\_Cache\_Smoke\_DRI\_Smoke\_N22.csv
%\item Fire\_Cache\_Smoke\_DRI\_Smoke\_N23.csv
%\item Fire\_Cache\_Smoke\_DRI\_Smoke\_N24.csv
%\item Fire\_Cache\_Smoke\_DRI\_Smoke\_N25.csv
%\item Fire\_Cache\_Smoke\_DRI\_Smoke\_N65.csv
%\item Fire\_Cache\_Smoke\_DRI\_Smoke\_N66.csv
%\item Fire\_Cache\_Smoke\_DRI\_Smoke\_N67.csv
%\item Fire\_Cache\_Smoke\_DRI\_Smoke\_N68.csv
%\item Fire\_Cache\_Smoke\_DRI\_Smoke\_N69.csv
%\item Fire\_Cache\_Smoke\_DRI\_Smoke\_N84.csv
%\item Fire\_Cache\_Smoke\_DRI\_Smoke\_N86.csv
%\item Fire\_Cache\_Smoke\_DRI\_Smoke\_N215.csv
%\item Fire\_Cache\_Smoke\_DRI\_Smoke\_N216.csv
%\item Fire\_Cache\_Smoke\_DRI\_Smoke\_N217.csv
%\item Fire\_Cache\_Smoke\_DRI\_Smoke\_E\_BAM\_52.csv
%\item Fire\_Cache\_Smoke\_DRI\_Smoke\_E\_BAM\_65.csv
%\item Fire\_Cache\_Smoke\_DRI\_Smoke\_E-BAM\_231.csv
%\item Fire\_Cache\_Smoke\_DRI\_Smoke\_E-BAM\_840.csv
%\item Fire\_Cache\_Smoke\_DRI\_Smoke\_E-BAM\_866.csv
%\item Fire\_Cache\_Smoke\_DRI\_Smoke\_E-BAM\_925.csv
%\item Fire\_Cache\_Smoke\_DRI\_Smoke\_NCFS\_E-BAM\_N1.csv
%\item Fire\_Cache\_Smoke\_DRI\_Smoke\_NCFS\_E-BAM\_N2.csv
%\item Fire\_Cache\_Smoke\_DRI\_Smoke\_USFS\_R1-39.csv
%\item Fire\_Cache\_Smoke\_DRI\_Smoke\_USFS\_R1-52.csv
%\item Fire\_Cache\_Smoke\_DRI\_Smoke\_USFS\_R1-53.csv
%\item Fire\_Cache\_Smoke\_DRI\_Smoke\_USFS\_R1-306.csv
%\item Fire\_Cache\_Smoke\_DRI\_Smoke\_USFS\_R1-307.csv
%\item Fire\_Cache\_Smoke\_DRI\_Smoke\_USFS\_R2-69.csv
%\item Fire\_Cache\_Smoke\_DRI\_Smoke\_USFS\_R2-78.csv
%\item Fire\_Cache\_Smoke\_DRI\_Smoke\_USFS\_R2-264.csv
%\item Fire\_Cache\_Smoke\_DRI\_Smoke\_USFS\_R2-265.csv
%\item Fire\_Cache\_Smoke\_DRI\_Smoke\_USFS\_R3-28.csv
%\item Fire\_Cache\_Smoke\_DRI\_Smoke\_USFS\_R3-86.csv
%\item Fire\_Cache\_Smoke\_DRI\_Smoke\_USFS\_R5-39.csv
%\item Fire\_Cache\_Smoke\_DRI\_Smoke\_USFS\_R5-49.csv
%\item Fire\_Cache\_Smoke\_DRI\_Smoke\_USFS\_R8-33.csv
%\item Fire\_Cache\_Smoke\_DRI\_Smoke\_USFS\_R9-15.csv
%\item Fire\_Cache\_Smoke\_DRI\_Smoke\_USFS\_R9-16.csv
%\item Fire\_Cache\_Smoke\_DRI\_Smoke\_USFS\_R9-17.csv
%\item Fire\_Cache\_Smoke\_DRI\_Smoke\_USFS\_R9-60.csv
%\item Fire\_Cache\_Smoke\_DRI\_Smoke\_NPS\_Yosemite\_01\_California.csv
%\end{enumerate}

\subsubsection*{Processed/Cleaned Data File Names}

\begin{enumerate}[nolistsep]
\item
\item
\end{enumerate}

\subsection*{Download instructions}
\begin{enumerate}
\item For each file:
\begin{enumerate}[nolistsep]
\item \url{https://wrcc.dri.edu/cgi-bin/smoke.pl}
\item Hover over the appropriate drop-down menu and click on the monitor you want to download e.g., “Cache Monitors” then “Smoke \#11”
\item On the left-side menu, click on ``Data Details”
\item Set the starting date: January 1, 2008 (or as far back as it goes if it doesn’t go back to 2008)
\item Set the ending date: Last date possible%December 31, 2014 (or the last date possible if it ends before 2014)
\item Elements (ignore - default is to include all elements)
\item Options
\begin{enumerate}[nolistsep]
\item Excel (.xls) (It had html code in the file if I chose other options.)
\item Data Source: Original
\item Represent missing data as: -9999.
\item Include data flags: Yes
\item Date format: MM/DD/YYYY hh:mm
\item Time format: LST 0-23
\item Table Header: Column header short descriptions
\item Field Delimiter: comma (,)
\item Select the Units: Metric
\item Leave Sub interval windows set to: January 01, December 31, Hours: 00 and 24
\item Submit Info
\end{enumerate}
\item Open in excel (this takes several seconds and sometimes there is an alert dialog box, answer yes)
\item Check the following:
\begin{enumerate}[nolistsep]
\item The name of the monitor is in cell A1
\item The header is spread across rows 2-4
\item There are 34 columns of data (goes through columns ``AH” in excel)
\item Concentration in the 11th (``K”) columns
\end{enumerate}
\item Save as: Fire\_Cache\_Smoke\_DRI\_*.csv Where * is the monitor name with spaces replaced with underscore and \# symbols replaced with the letter ``N'', e.g., the file name for monitor “Smoke \#11” is “Fire\_Cache\_Smoke\_DRI\_Smoke\_N11.csv”. If a window pops up asking whether to keep the csv format, answer yes.
\item List the file names in the latex documentation (PM25\_Fire\_Cache\_Smoke\_Monitor\_Archive.tex)
\end{enumerate}

\item Once all files are downloaded locally

\begin{enumerate}[nolistsep]
\item Upload file to S3 bucket in the Earthlab-reid-group folder within the Fire\_Cache\_Smoke\_DRI subfolder \url{https://732215511434.signin.aws.amazon.com/console}

\end{enumerate}

\end{enumerate}

\subsubsection*{Original Data File Names and notes about monitors (downloaded February 26-27, 2019)}
% \renewcommand{\labelenumii}{\Roman{enumii}}
 \renewcommand{\labelenumii}{\arabic{enumii}}
\begin{enumerate}%[nolistsep]
\item Cache Monitors

\begin{enumerate}[nolistsep]
\item Smoke \#11: August 2010 -- December 2018; Fire\_Cache\_Smoke\_DRI\_Smoke\_N11.csv
\item Smoke \#13: January 2010 -- February 2019; Fire\_Cache\_Smoke\_DRI\_Smoke\_N11.csv
\item Smoke \#15: August 2010 -- December 2018; Fire\_Cache\_Smoke\_DRI\_Smoke\_N15.csv
\item Smoke \#16: June 2011 -- June 2018; Fire\_Cache\_Smoke\_DRI\_Smoke\_N16.csv
\item Smoke \#17: September 2010 -- July 2018; Fire\_Cache\_Smoke\_DRI\_Smoke\_N17.csv
\item Smoke \#19: August 2010 -- October 2018; Fire\_Cache\_Smoke\_DRI\_Smoke\_N19.csv
\item Smoke \#20: June 2011 -- October 2018; Fire\_Cache\_Smoke\_DRI\_Smoke\_N20.csv
\item Smoke \#21: April 2011 -- December 2018; Fire\_Cache\_Smoke\_DRI\_Smoke\_N21.csv
\item Smoke \#22: February 2011 -- November 2018; Fire\_Cache\_Smoke\_DRI\_Smoke\_N22.csv
\item Smoke \#23: March 2011 -- February 2019; Fire\_Cache\_Smoke\_DRI\_Smoke\_N23.csv * This file seems to have a few rows of data shifted by two columns. Those rows look like they could be problematic, so I'll leave them as-is and let the processing scripts remove them.
\item Smoke \#24: March 2011 -- October 2018; Fire\_Cache\_Smoke\_DRI\_Smoke\_N24.csv * This file seems to have a few rows of data shifted by two columns. Those rows look like they could be problematic, so I'll leave them as-is and let the processing scripts remove them.
\item Smoke \#65: March 2013 -- August 2018; Fire\_Cache\_Smoke\_DRI\_Smoke\_N65.csv
\item Smoke \#66: March 2012 -- October 2018; Fire\_Cache\_Smoke\_DRI\_Smoke\_N66.csv
\item Smoke \#67: January 2012 -- June 2018; Fire\_Cache\_Smoke\_DRI\_Smoke\_N67.csv
\item Smoke \#68: March 2012 -- November 2018; Fire\_Cache\_Smoke\_DRI\_Smoke\_N68.csv
\item Smoke \#69: January 2012 -- October 2018; Fire\_Cache\_Smoke\_DRI\_Smoke\_N69.csv
\item Smoke \#84: March 2013 -- July 2018; Fire\_Cache\_Smoke\_DRI\_Smoke\_N84.csv * This file seems to have a few rows of data shifted by a few columns. Assuming those rows could be problematic, I'll leave them as-is and let the processing scripts remove them.
\item Smoke \#215: January 2014 -- October 2018; Fire\_Cache\_Smoke\_DRI\_Smoke\_N215.csv
\item Smoke \#216: January 2014 -- February 2019; Fire\_Cache\_Smoke\_DRI\_Smoke\_N216.csv
\item Smoke \# 217: January 2014 -- October 2018; Fire\_Cache\_Smoke\_DRI\_Smoke\_N216.csv * This file seems to have a few rows of data shifted by a few columns. Assuming those rows could be problematic, I'll leave them as-is and let the processing scripts remove them.
\item Smoke E-BAM 231: November 2014 -- December 2018; Fire\_Cache\_Smoke\_DRI\_Smoke\_E-BAM\_231.csv
\item Smoke E-BAM 418: July 2017 -- November 2018; \textbf{PASSWORD PROTECTED, CAN'T DOWNLOAD}
\item Smoke E-BAM 591: July 2017 -- September 2017  \textbf{PASSWORD PROTECTED, CAN'T DOWNLOAD}
\item Smoke E-BAM 592: July 2017 -- August 2018 \textbf{PASSWORD PROTECTED, CAN'T DOWNLOAD}
\item Smoke E-BAM 840: October 2014 -- February 2019; Fire\_Cache\_Smoke\_DRI\_Smoke\_E-BAM\_840.csv
\item Smoke E-BAM 866: November 2014 -- November 2018; Fire\_Cache\_Smoke\_DRI\_Smoke\_E-BAM\_866.csv
\item Smoke E-BAM 882: July 2017 -- September 2018  \textbf{PASSWORD PROTECTED, CAN'T DOWNLOAD}
\item Smoke E-BAM 925: November 2014 -- February 2019; Fire\_Cache\_Smoke\_DRI\_Smoke\_E-BAM\_925.csv * This file seems to have a few rows of data shifted by a few columns. Assuming those rows could be problematic, I'll leave them as-is and let the processing scripts remove them.
\item Smoke E-BAM 969: July 2017 -- September 2017;  \textbf{PASSWORD PROTECTED, CAN'T DOWNLOAD}
\end{enumerate}

\item USFS Regional Monitors
\begin{enumerate}[nolistsep]
\item Smoke USFS R-39: February 2013 -- October 2018; Fire\_Cache\_Smoke\_USFS\_R1-39.csv
\item Smoke USFS R1-52: January 2013 -- February 2019; Fire\_Cache\_Smoke\_USFS\_R1-52.csv
\item Smoke USFS R1-53: February 2013 -- February 2019; Fire\_Cache\_Smoke\_USFS\_R1-53.csv
\item Smoke USFS R1-306: November 2014 -- February 2019; Fire\_Cache\_Smoke\_USFS\_R1-306.csv
\item Smoke USFS R1-307: November 2014 -- September 2017; Fire\_Cache\_Smoke\_USFS\_R1-307.csv
\item Smoke USFS R2-69: May 2013 -- February 2019; Fire\_Cache\_Smoke\_USFS\_R2-69.csv
\item Smoke USFS R2-78: April 2013 -- October 2017; Fire\_Cache\_Smoke\_USFS\_R2-78.csv
\item Smoke USFS R2-264: November 2014 -- October 2017; Fire\_Cache\_Smoke\_USFS\_R2-264.csv
\item Smoke USFS R2-265: December 2014 -- October 2018; Fire\_Cache\_Smoke\_USFS\_R2-264.csv
\item Smoke USFS R2-922: June 2015 -- June 2018; Fire\_Cache\_Smoke\_USFS\_R2-922.csv
\item Smoke USFS R2-923: June 2015 -- October 2016; Fire\_Cache\_Smoke\_USFS\_R2-923.csv
\item Smoke USFS R2-924: June 2015 -- February 2019; Fire\_Cache\_Smoke\_USFS\_R2-924.csv  (website claims August of 1941 has data, but this is highly dubious.)
\item Smoke USFS R3-28: March 2013 -- October 2018; Fire\_Cache\_Smoke\_USFS\_R3-28.csv  * This file seems to have a few rows of data shifted by a few columns. Assuming those rows could be problematic, I'll leave them as-is and let the processing scripts remove them.
\item Smoke USFS R3-86: March 2018 -- February 2019; Fire\_Cache\_Smoke\_USFS\_R3-86.csv
\item Smoke USFS R5-39: June 2013 -- July 2014; Fire\_Cache\_Smoke\_USFS\_R5-39.csv
\item Smoke USFS R5-49: June 2013 -- July 2016; Fire\_Cache\_Smoke\_USFS\_R5-49.csv * concentrations are all 0 or -9999 ug/m3. Air Flow is correspondingly 0 or -9999 L/min, so all of these data will be removed by the processing scripts. 
\item Smoke USFS R8-33: December 2014 -- January 2017; Fire\_Cache\_Smoke\_USFS\_R8-33.csv
\item Smoke USFS R8-34: September 2015 -- August 2016; Fire\_Cache\_Smoke\_USFS\_R8-34.csv (website claims August of 1941 has data, but this is highly dubious.)
\item Smoke USFS R8-35: August 2016 -- July 2017; Fire\_Cache\_Smoke\_USFS\_R8-35.csv
\item Smoke USFS R8-55: November 2016 -- July 2017; \textbf{PASSWORD PROTECTED, CAN'T DOWNLOAD}
\item Smoke USFS R8-56: November 2016 -- July 2017; \textbf{PASSWORD PROTECTED, CAN'T DOWNLOAD}
\item Smoke USFS R9-15: February 2013 -- April 2018;  Fire\_Cache\_Smoke\_USFS\_R9-15.csv
\item Smoke USFS R9-16: February 2013 -- May 2018; Fire\_Cache\_Smoke\_USFS\_R9-16.csv
\item Smoke USFS R9-17: February 2013 -- May 2018; Fire\_Cache\_Smoke\_USFS\_R9-17.csv
\item Smoke USFS R9-60: October 2012 -- July 2018; Fire\_Cache\_Smoke\_USFS\_R9-60.csv * This file seems to have a few rows of data shifted by a few columns. Assuming those rows could be problematic, I'll leave them as-is and let the processing scripts remove them.
\item Smoke USFS 3015: December 2015 -- February 2019; Fire\_Cache\_Smoke\_USFS\_3015.csv
\item Smoke USFS 3016: May 2016 -- February 2019; Fire\_Cache\_Smoke\_USFS\_3016.csv (website claims 1941 has data, but this is highly dubious.)
\item Smoke USFS R9-3017: December 2015 -- February 2017; Fire\_Cache\_Smoke\_USFS\_R9-3017.csv
\item Smoke USFS R9-3018: January 2016 -- February 2017; Fire\_Cache\_Smoke\_USFS\_R9-3018.csv

\end{enumerate}

\item Miscellaneous Monitors
\begin{enumerate}[nolistsep]
\item Smoke \#25: January 2011 -- September 2015; Fire\_Cache\_Smoke\_DRI\_Smoke\_N25.csv * This file seems to have a few rows of data shifted by a few columns. Assuming those rows could be problematic, I'll leave them as-is and let the processing scripts remove them.
\item Smoke \#86: October 2012 -- February 2019 Fire\_Cache\_Smoke\_DRI\_Smoke\_N86.csv
\item Smoke E\_BAM 52: April 2012 -- April 2015; Fire\_Cache\_Smoke\_DRI\_Smoke\_E-BAM\_52.csv
\item Smoke E\_BAM 65: June 2013 -- September 2015; Fire\_Cache\_Smoke\_DRI\_Smoke\_E-BAM\_65.csv * This file seems to have a few rows of data shifted by a few columns. Assuming those rows could be problematic, I'll leave them as-is and let the processing scripts remove them.
\item FWS Smoke \#1: June 2012 -- November 2018; Fire\_Cache\_Smoke\_DRI\_FWS\_Smoke\_N1.csv
\item Smoke NCFS E-BAM \#1: June 2014 -- December 2016; * This file has 10 fewer columns of data that most of the files, which have 34, and the ordering of the columns that are there is different. Not sure if this will cause a problem when compiling the data. Fire\_Cache\_Smoke\_DRI\_Smoke\_NCFS\_E\_BAM\_N1.csv
\item Smoke NCFS E-BAM \#2: June 2014 -- February 2015; Fire\_Cache\_Smoke\_DRI\_Smoke\_NCFS\_E-BAM\_N2.csv * This file has 10 fewer columns of data that most of the files, which have 34, and the ordering of the columns that are there is different. Not sure if this will cause a problem when compiling the data. It is a short file and doesn't appear to have any days of data that will pass the quality checks (negative concentrations, too few hourly observations within a day).
\item Smoke NCFS E-BAM \#3: June 2014 -- February 2015; \textbf{PASSWORD PROTECTED, CAN'T DOWNLOAD}
\item Smoke NPS Yosemite 01 California: September 2014 -- Sepember 2018; Fire\_Cache\_Smoke\_DRI\_Smoke\_NPS\_Yosemite\_01\_California.csv
\item RSF Smoke Monitor 1: November 2015 -- July 2016; Fire\_Cache\_Smoke\_DRI\_RSF\_Smoke\_Monitor\_1.csv
\item Lolo NF Smoke Monitor \#1: February 2016 -- October 2018;  \textbf{PASSWORD PROTECTED, CAN'T DOWNLOAD}
\item Lolo NF Smoke Monitor \#2: February 2016 -- April 2016;  \textbf{PASSWORD PROTECTED, CAN'T DOWNLOAD}

\end{enumerate}

\end{enumerate}
