\subsection{PM2.5 data from CalNex 2010}
\url{https://esrl.noaa.gov/csd/groups/csd7/measurements/2010calnex/Ground/DataDownload/index.php?page=/csd/groups/csd7/measurements/2010calnex/Ground/DataDownload/}

\subsubsection{Data policy}

  Please check this box to signify agreement with our data policy. Then click the Submit button below.
Data Use Policy

These NOAA Chemical Sciences Division (CSD) field project data are made freely available to the public and the scientific community, and are the product of extensive research and effort to maintain and improve their accuracy and quality. However, the availability of these data does not constitute publication, and NOAA CSD and their collaborating partners require citable outputs from their research to ensure its continued support. We therefore expect all users of this data to ensure that the responsible scientists receive fair credit for their work, and are offered the opportunity to contribute to the research uses of the data as they deem appropriate.

Accordingly, we ask that all users note and adhere to the following guidelines and procedures when using these data:

    These data are freely available for exploratory analysis. At such time as a journal publication or conference presentation is planned using these data, the relevant PIs of measurements included in the analysis should be informed of the nature and aims of the research project and the intended use of the data. PI contact details are given in the header files of the ICARTT-formatted data.
    Contacting the PIs will ensure they have adequate foreknowledge of the proposed research and thus the opportunity to contribute as appropriate to the use of CSD field project data in the proposed research project.
    If the PI makes a significant intellectual contribution to the research, or if the data are essential to the work, or if an important result or conclusion depends on the data, co−authorship would normally be expected. This should be discussed at an early stage in the work.
    Manuscripts using the data with NOAA field project co−authors should be sent to the coauthors for review well before (e.g. 4 weeks) they are submitted for publication, to ensure that the quality and limitations of the data are accurately represented and the coauthors have adequate time to provide input.
\subsubsection{Other Info}    
Data manager: kenneth.c.aikin@noaa.gov 